ECE 657A Project Report

### 2016-04-04 project report/LNCS-template/paper.tex
report

%Single insitute
\author{Laura McCrackin (20262085),Yuzhou Wang (20609396) \and Tianhui Huang (20587328)}
%If there are too many authors, use \authorrunning
%\authorrunning{First Author et al.}
\institute{University of Waterloo}

@@

\section{Dataset}
We used the Machine Comprehension Test (MCTest) dataset created by Microsoft [1]. The authors of stories are all workers, residing in the United States. The average worker is 36 years old, more educated than the United States population in general (Paolacci et al., 2010), and the majority of workers are female. Workers were instructed to write a short (150-300 words) fictional story, and to write as if for a child in grade school. Workers were also asked to provide four reading comprehension questions pertaining to their story and, for each, four multiple-choice answers. Workers were requested to provide 'reasonable' incorrect answers that at least include words from the story so that their solution is not trivial. Finally, workers were asked to design their questions and answers such that at least two of the four questions required multiple sentences from the story to answer them. That is, for those questions it should not be possible to find the answer in any individual sentence. 
The MCTest corpus contains two sets of stories, named MC160 and MC500, and containing 160 and 500 stories respectively. MC160 was gathered first, then some improvements were made before gathering MC500. Adding a Grammar Test to form the MC500. 
In addition to the details described above, MC160 workers were given a target elementary grade school level (1-4) and a sample story matching that grade level5. 
For the story generate, they ensured that the data is the same quality as another set and also limited the text to children stories, so that it could be easily understand.The  vocabulary is also limited: the lowercase words in the story, questions, and answers were stemmed from list of approximately 8000 words that a 7 year old is likely to know. Multiple-sentence questions: At least two of the questions need multiple sentences to answer. As each story is fictional, the answers can only be found in the story itself, which requires high-level machine comprehension without any world knowledge.

@@

\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../parsing.png}
		\caption{ROC}
		\label{figure 1:Frame-Semantic Parsing}
	\end{subfigure}

\end{figure}

@@

Other people also have the idea of comprehension with Syntax, Frames, and Semantics method.Semantic: frame semantic parsing (Das et al., 2014) is aimed to extract frame-specific predicate-argument structures from sentences[3].
Syntax: given each candidate answer, we attempt to transform the question to a statement using the extraction rules[4]. We could see figure 2 for sematic and figure 3 for syntax.
\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../sematic.png}
		\caption{ROC}
		\label{figure 2:sematic parsing}
	\end{subfigure}

\end{figure}

\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../syntax.png}
		\caption{ROC}
		\label{figure 3:syntax}
	\end{subfigure}

\end{figure}

@@

Comprehension with Discourse Relations[5].The model jointly identifies relevant sentences, establishes relations between them and predicts an answer. The key idea is to implant discourse analysis into a joint model for comprehension. As we could see in picture 4.And the drawback of this model is that the accuracy varies significantly according to the question type. Which means not really stable. 
\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../disclosure.png}
		\caption{ROC}
		\label{figure 4:disclosure method}
	\end{subfigure}

\end{figure}

Comprehension for Learning Answer-Entailing Structures[6].We posit that there is a hidden (latent) structure that explains the relation between the question, correct answer, and text. For this given structure, the correctness of the answer is evident. Since the structure is latent, it must be inferred. Firstly, we should presents a unified max-margin framework that learns to find these hidden structures (given a corpus of question-answer pairs), and then uses what it learns to answer machine comprehension questions on novel texts. We could see this from figure 5. But the drawback of this method is that since inference is cheaply modelled via alignment structure, we lack the ability to deeply reason about facts or numbers. 
\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../disclosure.png}
		\caption{ROC}
		\label{figure 5:answer entailing method}
	\end{subfigure}

\end{figure}

@@

\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../LSTM.png}
		\caption{ROC}
		\label{figure 6:LSTM}
	\end{subfigure}

\end{figure}

The Impatient Reader focuses on the passages of a context document that are most likely to inform the answer to the query. We can go further by equipping the model with the ability to reread from the document as each query token is read. The result is an attention mechanism that allows the model to recurrently accumulate information from the document as it sees each query token, ultimately outputting a final joint document query representation for the answer prediction. We could see figure 7 for impatient reader.
\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../impa.png}
		\caption{ROC}
		\label{figure 7:impatient reader}
	\end{subfigure}

\end{figure}

The Attentive Reader can be viewed as a generalization of the application of Memory Networks to question answering. That model employs an attention mechanism at the sentence level where each sentence is represented by a bag of embeddings. This model could fix the bottleneck for the width of different words. This attention model first encodes the document and the query using separate bidirectional single layer LSTMs. This task has been tricky because of the number of parameters that must be fine-tuned.
Although this method cannot be backwards checking as impatient reader but according to some article, these two methods have the similar results, so our group used this model. We could see figure 8 for attentive model.
\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../attentive.png}
		\caption{ROC}
		\label{figure 8:attentive model}
	\end{subfigure}

\end{figure}

\section{Description of the project task and the used methods}
For data preprocessing, we use python NLTK library.
For deep learning part, we use blocks and fuels, Theano framework for deep learning part. 
Blocks and fuel[10] are two Python frameworks to train neural networks on large datasets. Blocks is based on Theano, a linear algebra compiler with CUDA-support (Bastien et al., 2012; Bergstra et al., 2010). It facilitates the training of complex neural network models by providing parametrized Theano operations, attaching metadata to Theano symbolic computational graph, and providing an extensive set of utilities to assist training the networks, e.g. training algorithms, logging, monitoring, visualization, and serialization. Fuel provides a standard format for machine learning datasets. It allows the user to easily iterate over large datasets, performing many types of pre-processing on the fly[10].
Blocks and Fuel are being developed by the Montreal Institute of Learning Algorithms (MILA) at the University of Montreal. Their focus lies on quick prototyping of complex neural network models. 
Instead of introducing new abstract objects representing 'models' or 'layers'. Blocks annotates the theano computational graph, maintaining the flexibility of theano while making large models manageable. 
Data processing is an integral part of training neural networks, which is not addressed by many of the aforementioned frameworks. Fuel aims to fill this gap. It provides tools to download datasets and iterate/preprocess them efficiently.

Theano is a popular choice for the implementation of neural networks (see e.g. Goodfellow et al. (2013b); Pascanu et al. (2013)). Blocks and many other libraries, such as Pylearn2 (Goodfellow et al., 2013a), build on Theano by providing reusable components that are common in neural networks, such as linear transformations followed by non-linear activations, or more complicated components such as LSTM units. In Blocks these components are referred to as 'bricks' or 'parametrized Theano operations'. 
Blocks comes with a large number of 'bricks'. 
The gradient descent training algorithm in Blocks is composed of different 'step rules' that modify the descent direction (learning rate scaling, momentum, gradient clipping, weight norm clipping, etc.). A variety of algorithms such as AdaGrad, ADADELTA, Adam, RMSProp are available as step rules. But in our project, we use gradient descent algorithm.
The goal of fuel is to provide a common interface to a variety of data formats and published datasets such as MNIST, CIFAR-10, ImageNet, etc. while making it easy for users to write an interface to new datasets. 
Blocks relies on Fuel for its data interface, but Fuel can easily be used by other machine learning frameworks that interface with datasets. 
Fuel offers built-in scripts that automate the task of downloading datasets, (similar to e.g. skdata1) and converting them to Fuel HDF5 specification. 
The fuel download script is used to download raw data files. Downloading the raw MNIST data files is as easy as typing fuel download mnist. The fuel convert script is used to convert raw data files into HDF5-format. 
Reproducibility being an important feature of both Fuel and Blocks, the fuel convert script automatically tags all files it creates with relevant module and interface versions and the exact command that was used to generate these files. Inspection of this metadata is done with the fuel info script. 
Theano is a compiler for mathematical expressions in Python that combines the convenience of NumPy syntax with the speed of optimized native machine language. The user composes mathematical expressions in a high-level description that mimics NumPy syntax and semantics, while being statically typed and functional (as opposed to imperative). These expressions allow Theano to provide symbolic differentiation. [11]
Theano was introduced to the machine learning community by Bergstra et al. (2010) as a CPU and GPU mathematical compiler, demonstrating how it can be used to symbolically define mathematical functions, automatically derive gradient expressions, and compile these expressions into executable functions that outperform implementations using other existing tools[12].
\section{compare of original method and the method we used}
The Attentive Reader can be viewed as a generalisation of the application of Memory Networks to question answering. That model employs an attention mechanism at the sentence level where each sentence is represented by a bag of embeddings. The Attentive Reader employs a finer grained token level attention mechanism where the tokens are embedded given their entire future and past context in the input document. 
The representation r of the document d is formed by a weighted sum of these output vectors. These weights are interpreted as the degree to which the network attends to a particular token in the document. Given this attention score the embedding of the document r is computed as the weighted sum of the token embeddings.

@@

We define a new method to determine which possible answer is the correct one. (function) That is, the correct answer should be the most similar to the most highly attended words in the story. We use the similarity metric (function) for a multiple choice answer of length n words. Take the weighted average of the attention each word from the multiple choice answer has within the story. If a word in the answer is not in the story, we then chooce to use word distance from the closest attended word as apenalty.

\section{run time}
As for the run time, and computational complexity. Original Attentive Reader: trained for 2-4 days using two NVIDIA Titan Black GPUs (PassMark score 8,667 each)
Our setup: one NVIDIA GTX 660 GPU (PassMark score 4,120) inside older machine: Core 2 Quad Q8300, 8GB DDR2 PC6400 RAM. And the training time is around one day.
For result, we first calculate weight matrix multiply vector embedding matrix for each word, and choose the highest possibility. The higher the possibility it is, the more colorful the words could be.

@@

\begin{inparaenum}
	\item using stop words library to remove stop words
	\item using regular expression
	\item define a function and by recursion to convert a number into a verb
	\item using library to deal with stem words
	\item using lemmatizatio: Returns the input word unchanged if it cannot be found in WordNet.
	\item dealing with rawfile and answer file input. To become,
	\item getting the entities.
	\item preprocessing both questions and answers
\end{inparaenum}

@@

Brackets work as designed:
<test>

The symbol for powerset is now correct: $\powerset$ and not a Weierstrass p ($\wp$).

\begin{inparaenum}
\item All these items...
\item ...appear in one line
\item This is enabled by the paralist package.
\end{inparaenum}

``something in quotes'' using plain tex or use \enquote{the enquote command}.

@@

\subsubsection*{Acknowledgments}
...

In the bibliography, use \texttt{\textbackslash textsuperscript} for ``st'', ``nd'', ...:
E.g., \enquote{The 2\textsuperscript{nd} conference on examples}. \cite{richardson2013mctest}
When you use \href{http://www.jabref.org}{JabRef}, you can use the clean up command to achieve that.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{splncs03}
\bibliography{paper}

%All links were last followed on October 5, 2014.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%% template for figure and table
\begin{figure}
	Simple Figure
	\caption{ Figure}
	\label{fig:simple}
\end{figure}

\begin{table}
	\caption{Simple Table}

	\label{tab:simple}
	Simple Table
\end{table}
%%%%%%%%%%%%%%%%%%
cref Demonstration: Cref at beginning of sentence, cref in all other cases.

\Cref{fig:simple} shows a simple fact, although \cref{fig:simple} could also show something else.

\Cref{tab:simple} shows a simple fact, although \cref{tab:simple} could also show something else.

\Cref{sec:intro} shows a simple fact, although \cref{sec:intro} could also show something else.
%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%Single insitute
\author{Laura McCrackin (20262085),  Tianhui Huang (20587328) \and Yuzhou Wang (20609396)}
%If there are too many authors, use \authorrunning
%\authorrunning{First Author et al.}
\institute{University of Waterloo}

@@

\section{Dataset}
We used the Machine Comprehension Test (MCTest) dataset created by Microsoft [1]. The authors of stories are all workers, residing in the United States. The average worker is 36 years old, more educated than the United States population in general, and the majority of workers are female. Workers were instructed to write a short fictional story, and to write as if for a child in grade school. Workers were also asked to provide four reading comprehension questions pertaining to their story and, for each, four multiple-choice answers. Workers were requested to provide 'reasonable' incorrect answers that at least include words from the story so that their solution is not trivial. Finally, workers were asked to design their questions and answers such that at least two of the four questions required multiple sentences from the story to answer them. That is, for those questions it should not be possible to find the answer in any individual sentence. 
The MCTest corpus contains two sets of stories, named MC160 and MC500, and containing 160 and 500 stories respectively. MC160 was gathered first, then some improvements were made before gathering MC500. Adding a Grammar Test to form the MC500. 
In addition to the details described above, MC160 workers were given a target elementary grade school level (1-4) and a sample story matching that grade level5. 
For the story generate, they ensured that the data is the same quality as another set and also limited the text to children stories, so that it could be easily understand.The  vocabulary is also limited: the lowercase words in the story, questions, and answers were stemmed from list of approximately 8000 words that a 7 year old is likely to know. Multiple-sentence questions: At least two of the questions need multiple sentences to answer. As each story is fictional, the answers can only be found in the story itself, which requires high-level machine comprehension without any world knowledge.

@@

\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../pic/parsing.png}

		\label{figure 1:Frame-Semantic Parsing}
	\end{subfigure}	
\end{figure}

%\begin{figure}[p]
%	\centering
%	\begin{subfigure}{.5\textwidth}
%		\centering
%		\includegraphics[width=1\linewidth]{../images-update/1-(3)-2.png}
%		\caption{ROC}
%		\label{fig:sub1}
%	\end{subfigure}

%\end{figure}

@@

Other people also have the idea of comprehension with Syntax, Frames, and Semantics method.Semantic: frame semantic parsing is aimed to extract frame-specific predicate-argument structures from sentences[3].
Syntax: given each candidate answer, we attempt to transform the question to a statement using the extraction rules[4]. We could see figure 2 for sematic and figure 3 for syntax.
%\begin{figure}[p]
%	\centering
%	\begin{subfigure}{.5\textwidth}
%		\centering
%		\includegraphics[width=1\linewidth]{../pic/sematic.png}
%		\caption{ROC}
%		\label{figure 2:sematic parsing}
%	\end{subfigure}

%\end{figure}

%\begin{figure}[p]
%	\centering
%	\begin{subfigure}{.5\textwidth}
%		\centering
%		\includegraphics[width=1\linewidth]{../pic/syntax.png}
%		\caption{ROC}
%		\label{figure 3:syntax}
%	\end{subfigure}	
%\end{figure}

@@

Comprehension with Discourse Relations[5].The model jointly identifies relevant sentences, establishes relations between them and predicts an answer. The key idea is to implant discourse analysis into a joint model for comprehension. As we could see in picture 4.And the drawback of this model is that the accuracy varies significantly according to the question type. Which means not really stable. 
%\begin{figure}[p]
%	\centering
%	\begin{subfigure}{.5\textwidth}
%		\centering
%		\includegraphics[width=1\linewidth]{../pic/disclosure.png}
%		\caption{ROC}
%		\label{figure 4:disclosure method}
%	\end{subfigure}
%\end{figure}

Comprehension for Learning Answer-Entailing Structures[6].We posit that there is a hidden (latent) structure that explains the relation between the question, correct answer, and text. For this given structure, the correctness of the answer is evident. Since the structure is latent, it must be inferred. Firstly, we should presents a unified max-margin framework that learns to find these hidden structures (given a corpus of question-answer pairs), and then uses what it learns to answer machine comprehension questions on novel texts. We could see this from figure 5. But the drawback of this method is that since inference is cheaply modelled via alignment structure, we lack the ability to deeply reason about facts or numbers. 
%\begin{figure}[p]
%	\centering
%	\begin{subfigure}{.5\textwidth}
%		\centering
%		\includegraphics[width=1\linewidth]{../pic/disclosure.png}
%		\caption{ROC}
%		\label{figure 5:answer entailing method}
%	\end{subfigure}
%\end{figure}

@@

%\begin{figure}[p]
%	\centering
%	\begin{subfigure}{.5\textwidth}
%		\centering
%		\includegraphics[width=1\linewidth]{../pic/LSTM.png}
%		\caption{ROC}
%		\label{figure 6:LSTM}
%	\end{subfigure}
%\end{figure}

The Impatient Reader focuses on the passages of a context document that are most likely to inform the answer to the query. We can go further by equipping the model with the ability to reread from the document as each query token is read. The result is an attention mechanism that allows the model to recurrently accumulate information from the document as it sees each query token, ultimately outputting a final joint document query representation for the answer prediction. We could see figure 7 for impatient reader.
%\begin{figure}[p]
%	\begin{subfigure}{.5\textwidth}
%		\centering
%		\includegraphics[width=1\linewidth]{../pic/impa.png}
%		\caption{ROC}
%		\label{figure 7:impatient reader}
%	\end{subfigure}
%\end{figure}

The Attentive Reader can be viewed as a generalization of the application of Memory Networks to question answering. That model employs an attention mechanism at the sentence level where each sentence is represented by a bag of embeddings. This model could fix the bottleneck for the width of different words. This attention model first encodes the document and the query using separate bidirectional single layer LSTMs. This task has been tricky because of the number of parameters that must be fine-tuned.
Although this method cannot be backwards checking as impatient reader but according to some article, these two methods have the similar results, so our group used this model. We could see figure 8 for attentive model.
%\begin{figure}[p]
%	\centering
%	\begin{subfigure}{.5\textwidth}
%		\centering
%		\includegraphics[width=1\linewidth]{../pic/attentive.png}
%		\caption{ROC}
%		\label{figure 8:attentive model}
%	\end{subfigure}	
%\end{figure}

\section{Description of the project task and the used methods}
For data preprocessing, we use python NLTK library.
For deep learning part, we use blocks and fuels, Theano framework for deep learning part. 
Blocks and fuel[10] are two Python frameworks to train neural networks on large datasets. Blocks is based on Theano, a linear algebra compiler with CUDA-support. It facilitates the training of complex neural network models by providing parametrized Theano operations, attaching metadata to Theano symbolic computational graph, and providing an extensive set of utilities to assist training the networks, e.g. training algorithms, logging, monitoring, visualization, and serialization. Fuel provides a standard format for machine learning datasets. It allows the user to easily iterate over large datasets, performing many types of pre-processing on the fly[10].
Blocks and Fuel are being developed by the Montreal Institute of Learning Algorithms (MILA) at the University of Montreal. Their focus lies on quick prototyping of complex neural network models. 
Instead of introducing new abstract objects representing 'models' or 'layers'. Blocks annotates the theano computational graph, maintaining the flexibility of theano while making large models manageable. 
Data processing is an integral part of training neural networks, which is not addressed by many of the aforementioned frameworks. Fuel aims to fill this gap. It provides tools to download datasets and iterate/preprocess them efficiently.

Theano is a popular choice for the implementation of neural networks. Blocks and many other libraries, such as Pylearn2, build on Theano by providing reusable components that are common in neural networks, such as linear transformations followed by non-linear activations, or more complicated components such as LSTM units. In Blocks these components are referred to as 'bricks' or 'parametrized Theano operations'. 
Blocks comes with a large number of 'bricks'. 
The gradient descent training algorithm in Blocks is composed of different 'step rules' that modify the descent direction (learning rate scaling, momentum, gradient clipping, weight norm clipping, etc.). A variety of algorithms such as AdaGrad, ADADELTA, Adam, RMSProp are available as step rules. But in our project, we use gradient descent algorithm.
The goal of fuel is to provide a common interface to a variety of data formats and published datasets such as MNIST, CIFAR-10, ImageNet, etc. while making it easy for users to write an interface to new datasets. 
Blocks relies on Fuel for its data interface, but Fuel can easily be used by other machine learning frameworks that interface with datasets. 
Fuel offers built-in scripts that automate the task of downloading datasets, (similar to e.g. skdata1) and converting them to Fuel HDF5 specification. 
The fuel download script is used to download raw data files. Downloading the raw MNIST data files is as easy as typing fuel download mnist. The fuel convert script is used to convert raw data files into HDF5-format. 
Reproducibility being an important feature of both Fuel and Blocks, the fuel convert script automatically tags all files it creates with relevant module and interface versions and the exact command that was used to generate these files. Inspection of this metadata is done with the fuel info script. 
Theano is a compiler for mathematical expressions in Python that combines the convenience of NumPy syntax with the speed of optimized native machine language. The user composes mathematical expressions in a high-level description that mimics NumPy syntax and semantics, while being statically typed and functional (as opposed to imperative). These expressions allow Theano to provide symbolic differentiation[11].
Theano was introduced to the machine learning community as a CPU and GPU mathematical compiler, demonstrating how it can be used to symbolically define mathematical functions, automatically derive gradient expressions, and compile these expressions into executable functions that outperform implementations using other existing tools[12].
\section{compare of original method and the method we used}
For preprocessing part:
1) split the story dataset into one story one file, and do the same thing on the related answer dataset 
2) label correct answers obtained from corresponding answer file
in each story file 
3) convert abbreviation using Regular Expression and numbers to words using a recrusive function implemented by ourselves on story, questions and answers in each story file 
4) lowercase all text of stories, tokenize them, then build a vocabulary file without repeat words
5) find out entities in each story and replace them with entity identifiers, then add the corresponding entity and entity identifier list below the questions
6) delete punctuations on the text of each story, the reason for doing this after step 5 is that punctuations will help to identify the entities 
7) remove stop words, lemmatization and stemming on each story dealing with NLTK library functions
8) preprocess both questions and answers using the entity list gained from step 5

The Attentive Reader can be viewed as a generalisation of the application of Memory Networks to question answering. That model employs an attention mechanism at the sentence level where each sentence is represented by a bag of embeddings. The Attentive Reader employs a finer grained token level attention mechanism where the tokens are embedded given their entire future and past context in the input document. 
The representation r of the document d is formed by a weighted sum of these output vectors. These weights are interpreted as the degree to which the network attends to a particular token in the document. Given this attention score the embedding of the document r is computed as the weighted sum of the token embeddings.

@@

For deep mind model output, we define function 1,for a given document(d) and query(q), we could estimate the probability of word a being the correct answer.We define a new method to determine which possible answer is the correct one. As we could see from function 2, that is, the correct answer should be the most similar to the most highly attended words in the story. We use the similarity metric, as we could see from function 3. For a multiple choice answer of length n words. Take the weighted average of the attention each word from the multiple choice answer has within the story. If a word in the answer is not in the story, we then chooce to use word distance from the closest attended word as apenalty.\newline
Function 1: \newline
 here some error for the function
%p(a|d,q) \propto exp (W(a) g(d,q)), a \epsilon V
W stands for weight, g stands for vector embedding and v stands for vocabulary \newline
Function 2: \newline
C=max[S(Ci,p(a|d,q))] \newline
here C is for correct choice, S is for similarity, Ci is for ith multiple choice answer, i from 1 to 4.
\newline
Function 3:\newline
%S(Ci,p(a|d,q))=\sum_{j=1}^{n} p(aj|d,q)/n    
here still a small problem and did not figure out yet
%S(Ci,p(a|d,q))=\sigma p(aj|d,q)/n
%%%%%%%
\section{run time}
As for the run time, and computational complexity. Original Attentive Reader: trained for 2-4 days using two NVIDIA Titan Black GPUs (PassMark score 8,667 each)
Our setup: one NVIDIA GTX 660 GPU  inside older machine: Core 2 Quad Q8300, 8GB DDR2 PC6400 RAM. And the training time is around one day.
For result, we first calculate weight matrix multiply vector embedding matrix for each word, and choose the highest possibility. The higher the possibility it is, the more colorful the words could be.

@@

1) split the story dataset into one story one file, and do the same thing on the related answer dataset 
2) label correct answers obtained from corresponding answer file
in each story file 
3) convert abbreviation using Regular Expression and numbers to words using a recrusive function implemented by ourselves on story, questions and answers in each story file 
4) lowercase all text of stories, tokenize them, then build a vocabulary file without repeat words
5) find out entities in each story and replace them with entity identifiers, then add the corresponding entity and entity identifier list below the questions
6) delete punctuations on the text of each story, the reason for doing this after step 5 is that punctuations will help to identify the entities 
7) remove stop words, lemmatization and stemming on each story dealing with NLTK library functions
8) preprocess both questions and answers using the entity list gained from step 5

@@

@@

\subsubsection*{Acknowledgments}

%In the bibliography, use \texttt{\textbackslash textsuperscript} for ``st'', ``nd'', ...:
%E.g., \enquote{The 2\textsuperscript{nd} conference on examples}. 
%When you use \href{http://www.jabref.org}{JabRef}, you can use the clean up command to achieve that.

\cite{richardson2013mctest}
\cite{hermann2015teaching}
\cite{wang2015machine}
\cite{yao2013answer}
\cite{narasimhan2015machine}
\cite{sachan2015learning}
\cite{hochreiter1997long}
\cite{gers2001lstm}
\cite{graves2009offline}
\cite{van2015blocks}
\cite{bergstra2010theano}
\cite{bastien2012theano}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{splncs03}
\bibliography{paper}

%\Cref{fig:simple} shows a simple fact, although \cref{fig:simple} could also show something else.
%\Cref{tab:simple} shows a simple fact, although \cref{tab:simple} could also show something else.
%\Cref{sec:intro} shows a simple fact, although \cref{sec:intro} could also show something else.
%%%%%%%%%%%%%%%%%%%%%%%%%
